---
title: "CompSciX 415.2 Homework 1"
author: "Yasmin Makoui"
date: "6/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
My Github repository for my assignment can be found at this URL: [https://github.com/yasi1362/CompScix-415-2-assignments](https://github.com/yasi1362/CompScix-415-2-assignments)


```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(mdsr)
```
Lets look at some data:

```{r}
data(WorldCities)
?WorldCities
```
**QUESTION 1: How many observations and variables are there in this data set? What are some of the variable names? Type up your answer in your document using complete sentences.

The WorldCities data set includes 10 variables, such as:
Code, name, latitude, longitude, country, country region, population, region code, region, date.

Lets take a glimpseof the data:
```{r}
glimpse(WorldCities)
```

Lets extract part of the data:
```{r}
WorldCities <- head(WorldCities, 200)
country_col <- WorldCities$country
unique(country_col)
```
**QUESTION 2: There is a column called region in the data set. Can you extract this and show only the unique values?
Unique values for country region:
```{r}
region_col <- WorldCities$region
unique(region_col)
```

Q3-
WorldCities %>% country_col %>% unique()

```{r}
data("WorldCities")
WorldCities <- head(WorldCities, 200)
country_col <- WorldCities$country
unique(country_col)
```

Q4 - 

```{r}
WorldCities %>% ggplot(aes(x = population)) + ylab( "something") + ggtitle("World Region and population") + geom_histogram()
```

