---
title: "COMPSCIX415.2 Homework 7"
author: "Yasmin Makoui"
date: "7/24/2018"
output: 
  html_document: 
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(mdsr)
```

##Exercise 1
####Load the train.csv dataset into R. How many observations and columns are there?
#####There are 81 columns and 1,460 observations.
```{r}
#import csv file
file_path_train <- '/Users/yasminmakoui/downloads/train.csv'
train_data <- read_csv(file = file_path_train)

#glimpse csv file
glimpse(train_data)
```

##Exercise 2
####Normally at this point you would spend a few days on EDA, but for this homework we will do some very basic EDA and get right to fitting some linear regression models.

####Our target will be SalePrice.

  *Visualize the distribution of SalePrice.
  *Visualize the covariation between SalePrice and Neighborhood.
  *Visualize the covariation between SalePrice and OverallQual.
  
##Exercise 3
####Our target is called SalePrice. First, we can fit a simple regression model consisting of only the intercept (the average of SalePrice). Fit the model and then use the broom package to

take a look at the coefficient,
compare the coefficient to the average value of SalePrice, and
take a look at the R-squared.

##Exercise 4
####Now fit a linear regression model using GrLivArea, OverallQual, and Neighborhood as the features. Don’t forget to look at  data_description.txt to understand what these variables mean. Ask yourself these questions before fitting the model:

What kind of relationship will these features have with our target?
Can the relationship be estimated linearly?
Are these good features, given the problem we are trying to solve?
After fitting the model, output the coefficients and the R-squared using the broom package.

Answer these questions:

How would you interpret the coefficients on GrLivArea and OverallQual?
How would you interpret the coefficient on NeighborhoodBrkSide?
Are the features significant?
Are the features practically significant?
Is the model a good fit?


##Exercise 5 (OPTIONAL - won’t be graded)
####Feel free to play around with linear regression. Add some other features and see how the model results change.

##Exercise 6
####One downside of the linear model is that it is sensitive to unusual values because the distance incorporates a squared term. Fit a linear model to the simulated data below (use y as the target and x as the feature), and look at the resulting coefficients and R-squared. Rerun it about 5-6 times to generate different simulated datasets. What do you notice about the model’s coefficient on x and the R-squared values?

sim1a <- tibble(
  x = rep(1:10, each = 3),
  y = x * 1.5 + 6 + rt(length(x), df = 2)
)
