---
title: "CompSciX 415.2 Homework 3"
author: "Yasmin Makoui"
date: "6/26/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mdsr)
library(tidyverse)
data(mpg)
ggplot2::mpg
```

```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
#> loading tidyverse: ggplot2
#> loading tidyverse: tibble
#> loading tidyverse: tidyr
#> loading tidyverse: readr
#> loading tidyverse: purrr
#> loading tidyverse: dplyr
#> Conflicts with tidy packages -------------------------------------------
#> filter(): dplyr, stats
#> lag(): dplyr, stats 
```

###Answers to Question in 3.8.1
#####1- It is difficult to see the mph in city and highway for each of these cars. we dont know what these cars are.
```{r}
ggplot(data = mpg, mapping = aes (x = cty, y = hwy)) + geom_point()
```
#####This graph gives more information about the corrolation of the cars and the mph
```{r}
ggplot(data = mpg, mapping = aes (x = cty,  fill = drv)) + geom_bar( position = "dodge")
```

#####2- Width and height control the amount of jittering
```{r}
?geom_jitter
ggplot(mpg, aes(cyl, hwy)) + geom_jitter()
ggplot(mpg, aes(cyl, hwy)) + geom_jitter(width = 0.25)
ggplot(mpg, aes(cyl, hwy)) + geom_jitter(width = 0.55, height = 0.55)
```
#####-3 "geom_count" is a variant geom_point that counts the number of observations at each location, then maps the count to point area. It useful when you have discrete data and overplotting. 
#####The jitter geom is a convenient shortcut for geom_point(position = "jitter"). It adds a small amount of random variation to the location of each point, and is a useful way of handling overplotting caused by discreteness in smaller datasets. As you can see below geom_count reveals more information abojut overlapping data.
```{r}
?geom_count
ggplot(mpg, aes(cty, hwy)) +
 geom_count()
ggplot(mpg, aes(cty, hwy)) +
 geom_jitter()
```
#####4 Position adjustment, either as a string, or the result of a call to a position adjustment function.

#####Defual position for boxplot is "dodge"
```{r}
?geom_boxplot
ggplot(mpg, aes(class, hwy)) + geom_boxplot()
```

###Answers to Question in 3.9.1
#####2- Modify axis, legend, and plot labels. Good labels are critical for making your plots accessible to a wider audience. Ensure the axis and legend labels display the full variable name.
```{r}
?labs()
ggplot(mtcars, aes(mpg, wt, colour = cyl)) + geom_point() + labs(colour = "Cylinders") + labs(x = "New x label")
```
#####4- geom_abline adds reference line (sometimes called rules) to a plot, either horizontal, vertical, or diagonal (specified by slope and intercept). These are useful for annotating plots. 
#####fixed scale coordinate system forces a specified ratio between the physical representation of data units on the axes. The ratio represents the number of units on the y-axis equivalent to one unit on the x-axis. The default, ratio = 1, ensures that one unit on the x-axis is the same length as one unit on the y-axis. Ratios higher than one make units on the y axis longer than units on the x-axis, and vice versa. coord_fixed is important to get a better visual of the data when both axis have the same measurment
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() +
  geom_abline() +
  coord_fixed()
?geom_abline
?coord_fixed
```

###Answers to Question in 4.4
#####1- The error is due to spelling
#####my_variable is spelled differently in the second line

#####2- 
```{r}
library(tidyverse)
```

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy))
```

```{r}
filter(mpg, cyl == 8)
```


```{r}
filter(diamonds, carat > 3)
```

###Answers to Question in 5.2.4
#####1- Please see below codes:


```{r}
library(nycflights13)
nycflights13::flights

filter(flights, arr_delay >= 120 , arr_delay == NA)
filter(flights, dest == "IAH" | dest == "HOU")
filter(flights, carrier == "UA" | carrier == "AA", carrier == "DL")
filter(flights, month == 7 | month == 8 | month == 9)
filter(flights, arr_delay > 120, dep_delay == 0)
filter(flights, dep_delay >= 60 & arr_delay < 30 )
filter(flights, dep_time >= "0600" | dep_time <= "1200")
```

#####3-
```{r}
filter(flights, is.na(dep_time))
```

#####4- NA is a logical constant of length 1 which contains a missing value indicator. NA can be coerced to any other vector type except raw. There are also constants NA_integer_, NA_real_, NA_complex_ and NA_character_ of the other atomic vector types which support missing values: all of these are reserved words in the R language.
```{r}
?NA
```


###Answers to Question in 5.4.1
#####1- Please see below codes:
```{r}
select(flights, dep_time, dep_delay, arr_time, arr_delay)
select(flights, contains("time"), contains("delay"))

```

#####3- one_of() function allows you to select variables based on their names.
```{r}
?one_of()
vars <- c("year", "month", "day", "dep_delay", "arr_delay")
```

