---
title: "CompSciX 415.2 Homework 3"
author: "Yasmin Makoui"
date: "6/26/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mdsr)
library(tidyverse)
data(mpg)
ggplot2::mpg
```

```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
#> loading tidyverse: ggplot2
#> loading tidyverse: tibble
#> loading tidyverse: tidyr
#> loading tidyverse: readr
#> loading tidyverse: purrr
#> loading tidyverse: dplyr
#> Conflicts with tidy packages -------------------------------------------
#> filter(): dplyr, stats
#> lag(): dplyr, stats 
```

###Answers to Question in 3.8
#####1- It is difficult to see the mph in city and highway for each of these cars. we dont know what these cars are.
```{r}
ggplot(data = mpg, mapping = aes (x = cty, y = hwy)) + geom_point()
```
#####This graph gives more information about the corrolation of the cars and the mph
```{r}
ggplot(data = mpg, mapping = aes (x = cty,  fill = drv)) + geom_bar( position = "dodge")
```

#####2- Width and height control the amount of jittering
```{r}
?geom_jitter
ggplot(mpg, aes(cyl, hwy)) + geom_jitter()
ggplot(mpg, aes(cyl, hwy)) + geom_jitter(width = 0.25)
ggplot(mpg, aes(cyl, hwy)) + geom_jitter(width = 0.55, height = 0.55)
```
#####-3 "geom_count" is a variant geom_point that counts the number of observations at each location, then maps the count to point area. It useful when you have discrete data and overplotting. 
##### The jitter geom is a convenient shortcut for geom_point(position = "jitter"). It adds a small amount of random variation to the location of each point, and is a useful way of handling overplotting caused by discreteness in smaller datasets. As you can see below geom_count reveals more information abojut overlapping data.
```{r}
?geom_count
ggplot(mpg, aes(cty, hwy)) +
 geom_count()
ggplot(mpg, aes(cty, hwy)) +
 geom_jitter()
```
#####4 Position adjustment, either as a string, or the result of a call to a position adjustment function.

##### Defual position for boxplot is "dodge"
```{r}
?geom_boxplot
ggplot(mpg, aes(class, hwy)) + geom_boxplot()
```

