---
title: "COMPSCIX 415.2 Homework 2"
author: "Yasmin Makoui"
date: "6/18/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
#> loading tidyverse: ggplot2
#> loading tidyverse: tibble
#> loading tidyverse: tidyr
#> loading tidyverse: readr
#> loading tidyverse: purrr
#> loading tidyverse: dplyr
#> Conflicts with tidy packages -------------------------------------------
#> filter(): dplyr, stats
#> lag(): dplyr, stats 
```
##Answers to questions 3.2.4 
#1- By running ggplot(data = mpg) the following empty graph will appear: 
```{r}
ggplot(data = mpg)
```

#2- 234 rows and 11 variables are in mpg data set
```{r}
ggplot2::mpg
?mpg
```

#3- drv variable are as follow: f = front-wheel drive, r = rear wheel drive, 4 = 4wd

#4- See below for scatterplot of hwy and cyl:
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = cyl, y = hwy)) + theme_bw()
```

#5- See below for scatterplot of class and drv. The following graph is not really helpful because it does not show a specific corrolation between the class of the car and how the wheels work. This information can not be used to make a conclusion. 
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = class, y = drv)) + theme_bw()
```

