---
title: "COMPSCIX 415.2 Homework 2"
author: "Yasmin Makoui"
date: "6/18/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
#> loading tidyverse: ggplot2
#> loading tidyverse: tibble
#> loading tidyverse: tidyr
#> loading tidyverse: readr
#> loading tidyverse: purrr
#> loading tidyverse: dplyr
#> Conflicts with tidy packages -------------------------------------------
#> filter(): dplyr, stats
#> lag(): dplyr, stats 
```
###Answers to questions 3.2.4 
#####1- By running ggplot(data = mpg) the following empty graph will appear: 
```{r}
ggplot(data = mpg)
```

#####2- 234 rows and 11 variables are in mpg data set
```{r}
ggplot2::mpg
?mpg
```

#####3- drv variable are as follow: f = front-wheel drive, r = rear wheel drive, 4 = 4wd

#####4- See below for scatterplot of hwy and cyl:
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = cyl, y = hwy)) + theme_bw()
```

#####5- See below for scatterplot of class and drv. The following graph is not really helpful because it does not show a specific corrolation between the class of the car and how the wheels work. This information can not be used to make a conclusion. 
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = class, y = drv)) + theme_bw()
```

###Answers to questions 3.3.1
#####1- The color in the graph below is not blue because color = "blue" is inside the aesthetics parentheses. r doesn't recognize "blue" as a variable in this data set.
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, color = "blue")) + theme_bw()
```
#####The following code will make the points blue.
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy), color = "blue") +theme_bw()
```

#####2- Categorical variables are: manufacturer, model, trans, drv, fl, class
##### Continuous variables are: displ, year, cyl, cty, hwy
##### You can find this information by typing ?mpg, or glimpse(mpg)
```{r}
glimpse(mpg)
```

###3- The graph with catehorical variable is useful. There are useful corrolations in thise graphs:
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = class , y = cty, color = trans)) +theme_bw() + ggtitle("With Categorical Variable - Color")
ggplot(data = mpg) + geom_point(mapping = aes(x = class , y = cty, size = trans)) +theme_bw() + ggtitle("With Categorical Variable - Size")
ggplot(data = mpg) + geom_point(mapping = aes(x = class , y = cty, shape = trans)) +theme_bw() + ggtitle("With Categorical Variable - Shape")

```

#####The graph with continuous variable is not useful. There are no useful corrolations in thise graphs: 
#####Shape can not be assigned to a continuous variable - R will respond back with an error
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = class , y = cty, color = displ)) +theme_bw() + ggtitle("With Continuous Variable - Color")
ggplot(data = mpg) + geom_point(mapping = aes(x = class , y = cty, size = displ)) +theme_bw() + ggtitle("With Continuous Variable - Size")
```

#####4- When assigning the same variable to multiple aesthetics, the graph does not provide meaningful information. 
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = class , y = cty, color = class)) +theme_bw() + ggtitle("With Continuous Variable - Color")
ggplot(data = mpg) + geom_point(mapping = aes(x = class , y = class, color = class)) +theme_bw() + ggtitle("With Continuous Variable - Color")
```

#####5- For shapes that have a border, you can colour the inside and the outside separately. Use the stroke aesthetic to modify the width of the border.
```{r}
?geom_point
ggplot(mtcars, aes(wt, mpg)) +
  geom_point(shape = 21, colour = "blue", fill = "pink", size = 5, stroke = 2) + theme_bw()
```

#####6- if you only map an aesthetic to something other than a variable name, R will respond with an error: geom_point requires the following missing aesthetics: x, y.

###Answers to questions 3.5.1
#####4- Advantages of using faceting is that we can break infomration to smaller pieces and get more details by categories. Disadvantages of faceting is that graphs dont tell one story about all the data. We can get lost in the details weithout reaching results. Also when working with big data, the number of graphs could be quite large, therefore not a useful way to get to a conclusion. 
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy)) + facet_wrap(~ class, nrow = 2)
```

#####5- In "facet_wrap"" "nrow"" means number of rows, and "ncol"" means number of columns. labeller is also a function makes it easy to assign different labellers to different factors. The labeller can be a function or it can be a named character vectors that will serve as a lookup table. "facet_grid" forms a matrix of panels defined by row and column facetting variables, so we can not modify columns and rows.

###Answers to questions 3.6.1
#####1- For line chart use geom_line, for boxplot chart use geom_boxplot, for a histogram chart use geom_histogram, for an area chart use geom_area.

#####2- It looks as expected.
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + geom_point() + geom_smooth(se = FALSE)
```

#####3- "show.legend" is logical. Should this layer be included in the legends? NA, the default, includes if any aesthetics are mapped. FALSE never includes, and TRUE always includes.
```{r}
ggplot(data = mpg) + geom_smooth(mapping = aes(x = displ, y = hwy, color = drv), show.legend = FALSE) 
```

#####4- "se" display confidence interval around smooth, TRUE by default. 

#####5- These graph look the same. The second code places maps the aesthetics twice for each geom, but the first code mapls the aesthetics once by including the mapping inside the ggplot function.
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + geom_point() + geom_smooth()

ggplot() + geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) + geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))
```

###Answers to questions 3.7.1
#####2- There are two types of bar charts: geom_bar makes the height of the bar proportional to the number of cases in each group (or if the weight aethetic is supplied, the sum of the weights). If you want the heights of the bars to represent values in the data, use geom_col instead. geom_bar uses stat_count by default: it counts the number of cases at each x position. geom_col uses stat_identity: it leaves the data as is.