---
title: "CompSciX 415.2 Homework 6"
author: "Yasmin Makoui"
date: "7/17/2018"
output: 
  html_document: 
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(mdsr)
library(mosaicData)
```

###1. What variables are in this data set?
  * outcome 
  * smoker
  * age

###2. How many observations are there and what does each represent? 
#####There are 1,314 observations on women who were classified as current smokers or as never having smoked. Each observation has represts the following:
  * outcome: survival status after 20 years: a factor with levels Alive Dead
  * smoker: smoking status at baseline: a factor with levels No Yes
  * age: age (in years) at the time of the first survey

###3. Create a table (use the R code below as a guide) and a visualization of the relationship between smoking status and outcome, ignoring age. What do you see? Does it make sense? 
```{r}
library(mosaicData)
library(tidyverse)
Whickham %>% count(smoker,outcome)
ggplot(Whickham, mapping = aes(x = smoker, fill = outcome)) + geom_bar()
```

4. Recode the age variable into an ordered factor with three categories: age <= 44, age > 44 & age <=
64, and age > 64. Now, recreate visualization from above, but facet on your new age factor. What do
you see? Does it make sense?
```{r}

```

