---
title: "CompSciX 415.2 HW4"
author: "Yasmin Makoui"
date: "6/26/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
###Baby Names HW
```{r load_packages, warning=FALSE, message=FALSE}
#import text file
library(tidyverse)
file_path_baby_names <- '/Users/yasminmakoui/downloads/baby_names.txt'
baby_names_data <- read_delim(delim = '|', file = file_path_baby_names)

#glimpse of imported text file
glimpse(baby_names_data)

#export csv file 
write_csv(baby_names_data, path = '/Users/yasminmakoui/downloads/baby_names_two.csv')

#import csv file
file_path_baby_names_two <- '/Users/yasminmakoui/downloads/baby_names_two.csv'
baby_names_two_data <- read_csv(file = file_path_baby_names_two)

#glimpse csv file
glimpse(baby_names_two_data)
```

###Answers to section 5.6.7
#####2- 
```{r}
library(tidyverse)
library(nycflights13)
not_cancelled <- flights %>% filter(!is.na(dep_delay), !is.na(arr_delay))

not_cancelled %>% count(dest)

not_cancelled %>% count(tailnum, wt = distance)
```
#####These codes show the same results as above without using count:
```{r}
not_cancelled %>% group_by(dest) %>%
  summarise(n())

not_cancelled %>% group_by(tailnum) %>%
  summarise(sum(distance))
```

#####4- Here are the observations of cancelled flights:
```{r}
by_day <- (flights %>% mutate(cancelled = (is.na(dep_delay) | is.na(arr_delay))) %>%
  group_by(year, month, day) %>% 
  summarise(prop_cancelled = mean(cancelled),
            avg_dep_delay = mean(dep_delay, na.rm = TRUE)))

library(ggplot2)


ggplot(data = by_day, aes(x = avg_dep_delay, prop_cancelled)) + 
  geom_jitter() + geom_smooth()

```

#####6 - The sort argument will sort the coutns from large to small in true.

###Answers to 10.5
#####1- mtcars print the row description as well
```{r}
print(mtcars)
as_tibble(mtcars)
```

#####2- tibble will automatically recycle inputs of lenght 1, and allows you to refer to variables that you just created. to create a table in dataframes we need to write longer codes since data frames dont work like tibble.
```{r}
df <- data.frame(abc = 1, xyz = "a")
df$x
df[, "xyz"]
df[, c("abc", "xyz")]
```
```{r}
vignette("tibble")
tb <- tibble(
  `1` = "abc",
  `a` = "xyz"
)
tb
```

#####3 - using the as.tbble function you can extract variables as tibble
```{r}
aaa <- "mpg"

as.tibble(aaa)
```

#####6 - You can control the default appearance with options:

#####options(tibble.print_max = n, tibble.print_min = m): if there are more than n rows, print only the first m rows. Use options(tibble.print_max = Inf) to always show all rows.

#####options(tibble.width = Inf) will always print all columns, regardless of the width of the screen.

###Answers to 12.3.3
#####2- The code returns with error since the year should have the back tick marks around them to be recognized as value in tidy. to fix it we can run the code below:
```{r}
table4a %>% 
  gather('1999', '2000', key = "year", value = "cases")
```

#####3 - spreading this fails because there are 2 different values for the same person and key. We need to delete one of the age observations for Phillip
```{r}
people <- tribble(
  ~name,             ~key,    ~value,
  #-----------------|--------|------
  "Phillip Woods",   "age",       45,
  "Phillip Woods",   "height",   186,
  "Jessica Cordero", "age",       37,
  "Jessica Cordero", "height",   156
)

people %>% spread(key = "key", value = "value")

```
#####4- We should use gather and variables are female and count
```{r}
preg <- tribble(
  ~pregnant, ~male, ~female,
  "yes",     NA,    10,
  "no",      20,    12
)


#tidy the tibble above
preg %>% gather("male", "female", key = female, male , value = count()) 

```

###Answers to 12.4.3
#####1 - extra: If sep is a character vector, this controls what happens when there are too many pieces. There are three valid options:
#####"warn" (the default): emit a warning and drop extra values.
#####"drop": drop any extra values without a warning.
#####"merge": only splits at most length(into) times

#####fill: If sep is a character vector, this controls what happens when there are not enough pieces. There are three valid options:
#####"warn" (the default): emit a warning and fill from the right
#####"right": fill with missing values on the right
#####"left": fill with missing values on the left
```{r}
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three") )

tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"))
```

#####2 - remove argument removes input column from output data frames if true. To retain the column of values that was united or separated, we set remove argument to false.

