---
title: "COMPSCIX 415.2 Homework 9/Final"
author: "Yasmin Makoui"
date: "8/7/2018"
output:
  html_document: 
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(mdsr)
library(broom)
library(ggmap)
library(forecast)
library(tseries)
library(RgoogleMaps)
library(leaflet)
library(rgdal)
```

##Exercise 1 - Sampling Distributions, Functions and For Loops (10 points)
```{r}
# sample size
samp_size <- 100
# set the rate parameter
samp_rate <- 1/10000

# take sample
rexp(n = samp_size, rate = samp_rate)
```

###STEP 1

####Write an R function that does the following:

####Takes a sample of size samp_size from this exponential distribution (samp_size is an input parameter for the function)
####Calculates the mean of that sample
####Calculates the standard deviation of that sample
####Returns the calculated mean and standard deviation as a list 

```{r}
samp_fun <- function(samp_size, samp_rate) {
  
  ...your code here...
  
  stats <- list(samp_avg = samp_avg, samp_std_dev = samp_std_dev)
  return(stats)
}
```

