---
title: "COMPSCIX 415.2 Homework 5/Midterm"
author: "Yasmin Makoui"
date: "7/10/2018"
output: 
  html_document: 
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(mdsr)
```

My Github repository for my midterm can be found at this URL: [https://github.com/yasi1362/CompScix-415-2-assignments/tree/master/Midterm](https://github.com/yasi1362/CompScix-415-2-assignments/tree/master/Midterm)

##The tidyverse packages
###Q1 
####Can you name which package is associated with each task below?
######Plotting - ggplot2
######Data munging/wrangling - dplyr 
######Reshaping(spreading & gathering) data - tidyr
######Importing/exporting data - readr

###Q2 
####Now can you name two functions that you’ve used from each package that you listed above for these tasks?
######Plotting: 
  * geom function -> geom_point()
  * theme function -> theme_bw()
  
######Data munging/wrangling:
  * summarise()
  * filter()

######Reshaping data:
  * gather()
  * spread()

######Importing/exporting data:
  * read_csv()
  * read_delim()

##R Basics
###Q1
####Fix this code with the fewest number of changes possible so it works:
#####My_data.name___is.too00ooLong! <- c( 1 , 2 , 3 )

#####! can not be used to name a variable
  
```{r}
My_data.name___is.too00ooLong <- c( 1 , 2 , 3 )
My_data.name___is.too00ooLong
```
###Q2
####Fix this code so it works:
#####my_string <- C('has', 'an', 'error', 'in', 'it)

##### c should not be capitalized, and the closing ' was missing for "it"
  
```{r}
my_string <- c('has', 'an', 'error', 'in', 'it')
my_string
```

###Q3
####Look at the code below and comment on what happened to the values in the vector.
#####my_vector <- c(1, 2, '3', '4', 5)
#####my_vector
##### [1] "1" "2" "3" "4" "5"

#####Since number 3 and 4 were inside quotes the values changed from numbers to characters. To keep the values as numbers we should not include the quotes around numbers.
```{r}
my_vector <- c(1, 2, 3, 4, 5)
my_vector
```

##Data import/export