---
title: "COMPSCIX 415.2 Homework 5/Midterm"
author: "Yasmin Makoui"
date: "7/10/2018"
output: 
  html_document: 
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(mdsr)
```

My Github repository for my midterm can be found at this URL: [https://github.com/yasi1362/CompScix-415-2-assignments/tree/master/Midterm](https://github.com/yasi1362/CompScix-415-2-assignments/tree/master/Midterm)

##The tidyverse packages
###Q1 
####Can you name which package is associated with each task below?
######Plotting - ggplot2
######Data munging/wrangling - dplyr 
######Reshaping(spreading & gathering) data - tidyr
######Importing/exporting data - readr

###Q2 
####Now can you name two functions that you’ve used from each package that you listed above for these tasks?
######Plotting: 
  * geom function -> geom_point()
  * theme function -> theme_bw()
  
######Data munging/wrangling:
  * summarise()
  * filter()

######Reshaping data:
  * gather()
  * spread()

######Importing/exporting data:
  * read_csv()
  * read_delim()

##R Basics
###Q1
####Fix this code with the fewest number of changes possible so it works:
#####My_data.name___is.too00ooLong! <- c( 1 , 2 , 3 )

#####! can not be used to name a variable
  
```{r}
My_data.name___is.too00ooLong <- c( 1 , 2 , 3 )
My_data.name___is.too00ooLong
```
###Q2
####Fix this code so it works:
#####my_string <- C('has', 'an', 'error', 'in', 'it)

##### c should not be capitalized, and the closing ' was missing for "it"
  
```{r}
my_string <- c('has', 'an', 'error', 'in', 'it')
my_string
```

###Q3
####Look at the code below and comment on what happened to the values in the vector.
#####my_vector <- c(1, 2, '3', '4', 5)
#####my_vector
##### [1] "1" "2" "3" "4" "5"

#####Since number 3 and 4 were inside quotes the values changed from numbers to characters. To keep the values as numbers we should not include the quotes around numbers.
```{r}
my_vector <- c(1, 2, 3, 4, 5)
my_vector
```

##Data import/export
###Q1
####1. Download the rail_trail.txt file from Canvas (in the Midterm Exam section) and successfully import it into R. Prove that it was imported successfully by including your import code and taking a glimpse of the result.
```{r}
#import text file
file_path_rail_trail_txt <- '/Users/yasminmakoui/downloads/rail_trail.txt'
rail_trail_data <- read_delim(delim = '|', file = file_path_rail_trail_txt)

#glimpse of imported text file
glimpse(rail_trail_data)
```


###Q2
####Export the file into a comma-separated file and name it “rail_trail.csv”. Make sure you define the path correctly so that you know where it gets saved. Then reload the file. Include your export and import code and take another glimpse.
```{r}
#export csv file 
write_csv(rail_trail_data, path = '/Users/yasminmakoui/downloads/rail_trail.csv')

#import csv file
file_path_rail_trail_csv <- '/Users/yasminmakoui/downloads/rail_trail.csv'
rail_trail_data_csv <- read_csv(file = file_path_rail_trail_csv)

#glimpse csv file
glimpse(rail_trail_data_csv)
```

##Visualization
###Q1
####Critique the graphic provided in midterm: give only three examples of what is wrong with this graphic. Be concise.
  1. The size of the circles do not represent the percentages. For example for women category the circle for the 20% is much smaller than the 72%, and it could be misleading.
  2. Each category does not add up to 100%.
  3. This visual does not show the total population in the study or the numbers of each category that participated in the study. The data could be skewed depending on who participate in this study.
  
  